$\pi$ with leftovers: \\ a mechanisation in Agda

### 2021-01-20 paper/paper.tex
Remove typing rules for PreCtx, Idxs, and Ctx

  \begin{mathpar}
    \datatype
    {n : \N}
    {\PreCtx_n : \Set}
    \; \textsc{PreCtx}

    \inferrule
        { }
        {[] : \PreCtx_{\constr{0}}}

        \inferrule
            {\gamma : \PreCtx_n \\ t : \Type}
            {\gamma \comma t : \PreCtx_{\suc n}}
  \end{mathpar}

@@

  A \emph{typing context} (last two rules above) is a length-indexed list of types, and is either empty $[]$ or the result of appending a type $t$ to an existing context $\gamma$r
\end{nidefinition}

\begin{nidefinition}[\textsc{Ctx}: usage contexts]
  A \emph{usage context} is a context $\Ctx_{idxs}$ of pairs of usage annotations that is indexed by a length-indexed context of indices $\Idxs_n$.
  A usage context is either empty $[]$ or the result or appending a usage annotation $x$ to an existing context $\Gamma$.
  \begin{mathpar}
    \datatype
    {n : \N}
    {\Idxs_n : \Set}
    \; \textsc{Idxs}

    \inferrule
        { }
        {[] : \Idxs_{\constr{0}}}

    \inferrule
        {idxs : \Idxs_n \\ idx : \Idx}
        {idxs \comma idx : \Idxs_{\suc n}}

    \datatype
    {idxs : \Idxs_n}
    {\Ctx_{idxs} : \Set}
    \; \textsc{Ctx}

    \inferrule
        { }
        {[] : \Ctx_{[]}}

    \inferrule
        {\Gamma : \Ctx_{idxs} \\ x : \Usage_{idx} ^{\func{2}}}
        {\Gamma \comma x : \Ctx_{idxs \comma idx}}
  \end{mathpar}

  We use the notation $\type{C}^{\func{2}}$ to stand for a $\type{C} \constr{\times} \type{C}$ pair of input and output multiplicities, respectively.
  Henceforth, we use $\lz$ to denote the multiplicity pair $0 \comma 0$, $\li$ for the pair $1 \comma 0$, $\lo$ for $0 \comma 1$, and $\lio$ for $1 \comma 1$.
  This notation was originally used in the linear \picalc{} \cite{KPT96,Sangio01}.
\end{nidefinition}

>>>>

@@

  A \emph{typing context} $\PreCtx_n$ is a length-indexed list of types that is either empty $\constr{[]}$ or the result of appending a type $\Type$ to an existing context.
\end{nidefinition}

\begin{nidefinition}[\textsc{Ctx}: usage contexts]
  A context of indices $\Idxs_n$ is a length-indexed list that is either empty $\constr{[]}$ or the result of appending an index $\Idx$ to an existing context.
  A \emph{usage context} is a context $\Ctx_{idxs}$ indexed by a context of indices $\Idxs_n$ that is either empty $\constr{[]}$ or the result or appending a usage annotation pair $\Usage_{idx}^{\func{2}}$ with index $idx$ to an existing context.
  We use the notation $\type{C}^{\func{2}}$ to stand for a $\type{C} \constr{\times} \type{C}$ pair of input and output multiplicities, respectively.
  Henceforth, we use $\lz$ to denote the multiplicity pair $0 \comma 0$, $\li$ for the pair $1 \comma 0$, $\lo$ for $0 \comma 1$, and $\lio$ for $1 \comma 1$.
  This notation was originally used in the linear \picalc{} \cite{KPT96,Sangio01}.
\end{nidefinition}
